Full waveform inversion and joint migration inversion with an automatic directional total variation constraint

### 2020-10-10 dtv/paper.tex
2020年10月 9日 星期五 22时22分12秒 CDT
2020年10月10日 星期六 09时57分00秒 CDT

%\documentclass[manuscript]{geophysics}
%	\usepackage{amsmath}
%	\usepackage{amssymb}
%	\usepackage{graphicx}
%	\usepackage{indentfirst}
%	\usepackage{lineno}
%	\usepackage{algorithm,algorithmic}
%	\usepackage{float}
%\begin{document}

@@

%\begin{center}
%\huge{\textbf{Full waveform inversion and joint migration inversion with an automatic directional total variation constraint}} 
%\end{center}

@@

The popular regularization methods include: quadratic \new{L2-norm-based}\old{L2-norm based} regularization, such as Tikhonov regularization \citep{Hu09}, and laplacian smoothing \citep{guitton2012constrained,qu162,qu2017simultaneous}, which tend to produce models with blurred discontinuities; non-quadratic \new{L1-norm-based}\old{L1-norm based} regularization, such as total variation (TV) \citep{anagaw2011full,qu161}, smooths the model by enhancing the sparsity of the spatial gradient of the velocity, thereby\old{,} preserving its edges. However, regular TV regularization only tends to reduce the horizontal and vertical gradients of each gridpoint in the model regardless of their structural direction. Thus, TV is not suitable where the local geologic structure has a dominant structural direction. Unlike general digital images, the spatial changes of the seismic model always have some specific geological structures, like tilted layers, faults, or edges of a salt body \citep{yangkang2017lsrtm,wujuan2018cg1,baimin2018cg,yangkang2018gji3}. \cite{bayram2012directional} proposed a directional TV method and applied it to digital image denoising. However, they only consider one single dominant direction for all pixels, which is obviously ineffective for \new{complex-textured}\old{complex textured} geologies. \new{Therefore, we propose a directional TV constraint based on a rough estimate of the subsurface image.}

@@

\plot{FWI_fig3}{width=0.9\textwidth}{FWI example: The inverted velocity using (a) regular FWI without any regularization, (b) FWI with conventional TV, and (c) FWI with directional TV. (d) The convergence diagrams of the data misfit as a function of iteration. The blue line denotes the inverted velocity using regular FWI without any regularization. The red line denotes the inverted velocity using FWI with conventional TV. The yellow line denotes the inverted velocity using FWI with directional TV.}

\plot{vel_profile-01}{width=0.9\textwidth}{FWI example: Comparison of different velocities at three locations. Velocity comparison at (a) \new{$X = 1000$ m}\old{$X = 1000 m$}, (b) \new{$X = 2000$ m}\old{$X = 2000 m$}, (c) \new{$X = 3000$ m}\old{$X = 3000 m$}. The purple line denotes the true velocity. The green line denotes the initial velocity. The blue line denotes the inverted velocity using regular FWI without any regularization. The red line denotes the inverted velocity using FWI with conventional TV. The yellow line denotes the inverted velocity using FWI with directional TV. The three locations are highlighted by the black dash lines in \new{Figure}\old{figure}~\ref{fig:FWI_fig3}a-c}.

@@

\bibliographystyle{seg}  % style file is seg.bst
\bibliography{2017_seg}

%\end{document}

>>>>

\published{Geophysics, 84, no. 2, (2019)}

@@

@@

The popular regularization methods include: quadratic \new{L2-norm-based}\old{L2-norm based} regularization, such as Tikhonov regularization \citep{Hu09}, and laplacian smoothing \citep{guitton2012constrained,qu162,qu2017simultaneous}, which tend to produce models with blurred discontinuities; non-quadratic \new{L1-norm-based}\old{L1-norm based} regularization, such as total variation (TV) \citep{anagaw2011full,qu161}, smooths the model by enhancing the sparsity of the spatial gradient of the velocity, thereby\old{,} preserving its edges. However, regular TV regularization only tends to reduce the horizontal and vertical gradients of each gridpoint in the model regardless of their structural direction. Thus, TV is not suitable where the local geologic structure has a dominant structural direction. Unlike general digital images, the spatial changes of the seismic model always have some specific geological structures, like tilted layers, faults, or edges of a salt body \citep{yangkang2017lsrtm,wujuan2018cg1,baimin2018cg,yangkang2020gji3}. \cite{bayram2012directional} proposed a directional TV method and applied it to digital image denoising. However, they only consider one single dominant direction for all pixels, which is obviously ineffective for \new{complex-textured}\old{complex textured} geologies. \new{Therefore, we propose a directional TV constraint based on a rough estimate of the subsurface image.}

@@

%original files
%\plot{FWI_fig3}{width=0.9\textwidth}{FWI example: The inverted velocity using (a) regular FWI without any regularization, (b) FWI with conventional TV, and (c) FWI with directional TV. (d) The convergence diagrams of the data misfit as a function of iteration. The blue line denotes the inverted velocity using regular FWI without any regularization. The red line denotes the inverted velocity using FWI with conventional TV. The pink line denotes the inverted velocity using FWI with directional TV.}

\inputdir{marm}
\multiplot{4}{vinv,vinv_tv,vinv_dtv,objs}{width=0.45\textwidth}{FWI example: The inverted velocity using (a) regular FWI without any regularization, (b) FWI with conventional TV, and (c) FWI with directional TV. (d) The convergence diagrams of the data misfit as a function of iteration. The blue line denotes the inverted velocity using regular FWI without any regularization. The red line denotes the inverted velocity using FWI with conventional TV. The yellow line denotes the inverted velocity using FWI with directional TV.}

\inputdir{./}
\plot{vel_profile-01}{width=0.9\textwidth}{FWI example: Comparison of different velocities at three locations. Velocity comparison at (a) \new{$X = 1000$ m}\old{$X = 1000 m$}, (b) \new{$X = 2000$ m}\old{$X = 2000 m$}, (c) \new{$X = 3000$ m}\old{$X = 3000 m$}. The purple line denotes the true velocity. The green line denotes the initial velocity. The blue line denotes the inverted velocity using regular FWI without any regularization. The red line denotes the inverted velocity using FWI with conventional TV. The yellow line denotes the inverted velocity using FWI with directional TV. The three locations are highlighted by the black dash lines in \new{Figure}\old{figure}~\ref{fig:FWI_fig3}a-c}.

@@

\bibliographystyle{seg}  % style file is seg.bst
\bibliography{dtv}
